---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# timetravel

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/Reckziegel/timetravel/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Reckziegel/timetravel/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of `timetravel` is to help users to perform the third step in Meucci’s Checklist: __Projection__.

## Installation

You can install the development version of `timetravel` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Reckziegel/timetravel")
```

## Usage

From __The Prayer__:

> ... The projection step is the process of obtaining the distribution at the investment horizon of the relevant risk drivers from the distribution of the invariants and additional information available at the current time T.

Let's say the statistician have already found [invariance](https://reckziegel.github.io/invariance/) in a time-series: 

```{r}
# Step 1: Quest for Invariance
library(tibble)

invariance <- as_tibble(diff(log(EuStockMarkets))) 
invariance
```

Then, the randomness of the "market" can be estimated with [uncover](https://reckziegel.github.io/uncover/):

```{r}
# Step 2: Estimation
library(uncover)

# Say... a Student-t distribution
fit <- fit_t(.invariant = invariance)
fit
```

A simulation of this characteristic process can be constructed with `simulate_margins`:

```{r}
fit_simul <- simulate_margins(model = fit, n = 100000)
fit_simul
```

The `timetravel` package provides the family of functions `project_*()` in order to make projection step easier: 

```{r}
# Step 3: Projection
library(timetravel)

prjct2 <- project_t(.invariant = fit_simul, .horizon = 2, .n = 100000)
prjct2

prjct5 <- project_t(.invariant = fit_simul, .horizon = 5, .n = 100000)
prjct5
```

In witch the `autoplot` method is available:

```{r}
library(ggplot2)

# 2 days ahead
autoplot(prjct2) + 
  scale_color_viridis_d(end = 0.75)

# 5 days ahead
autoplot(prjct5) + 
  scale_color_viridis_d(end = 0.75)
```

For more information on projection, please, see the reference page. 

## References

- Meucci, Attilio, ‘The Prayer’ Ten-Step Checklist for Advanced Risk and Portfolio Management (February 2, 2011). Available at SSRN: https://ssrn.com/abstract=1753788 or http://dx.doi.org/10.2139/ssrn.1753788
